### 2025-07-29 base-rates.qmd
20250729 - update URLs

The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `posttestProbability()` function that estimates the posttest probability of an event, given the [pretest probability](#sec-baseRate) and the [likelihood ratio](#sec-diagnosticLikelihoodRatio), or given the [pretest probability](#sec-baseRate) and the [sensitivity](#sec-sensitivity) (SN) and [specificity](#sec-specificity) (SP) of the test.

@@

A probability nomogram calculator is available from @Schwartz2006 at the following link: [http://araw.mede.uic.edu/cgi-bin/testcalc.pl](http://araw.mede.uic.edu/cgi-bin/testcalc.pl) (archived at <https://perma.cc/X8TF-7YBX>).
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `nomogrammer()` function that creates a nomogram plot using the [positive](#sec-positiveLikelihoodRatio) and [negative](#sec-negativeLikelihoodRatio) [likelihood ratio](#sec-diagnosticLikelihoodRatio) or using the [sensitivity](#sec-sensitivity) (SN) and [specificity](#sec-specificity) (SP) of the test, as adapted from @Chekroud2017:

>>>>

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `posttestProbability()` function that estimates the posttest probability of an event, given the [pretest probability](#sec-baseRate) and the [likelihood ratio](#sec-diagnosticLikelihoodRatio), or given the [pretest probability](#sec-baseRate) and the [sensitivity](#sec-sensitivity) (SN) and [specificity](#sec-specificity) (SP) of the test.

@@

A probability nomogram calculator is available from @Schwartz2006 at the following link: [http://araw.mede.uic.edu/cgi-bin/testcalc.pl](http://araw.mede.uic.edu/cgi-bin/testcalc.pl) (archived at <https://perma.cc/X8TF-7YBX>).
The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `nomogrammer()` function that creates a nomogram plot using the [positive](#sec-positiveLikelihoodRatio) and [negative](#sec-negativeLikelihoodRatio) [likelihood ratio](#sec-diagnosticLikelihoodRatio) or using the [sensitivity](#sec-sensitivity) (SN) and [specificity](#sec-specificity) (SP) of the test, as adapted from @Chekroud2017:

### 2025-07-29 basic-statistics.qmd
20250729 - update URLs

The mode is the most common/frequent value.
The mode of the values of 0, 0, 10, 15, 20, 30, and 1000 is `{r} exampleValues_mode`.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `Mode()` function for computing the mode of a set of data.

If you want to give some values more weight to others, you can calculate a weighted mean and a weighted median (or other quantile), while assigning a weight to each value.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains various functions for computing the weighted median (i.e., a weighted quantile at the 0.5 quantile, which is equivalent to the 50th percentile) based on @Akinshin2023.
Because some projections are outliers, we use a trimmed version of the weighted Harrell-Davis quantile estimator for greater robustness.

@@

If you want to give some values more weight to others, you can calculate weighted quantiles, while assigning a weight to each value.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains various functions for computing weighted quantiles based on @Akinshin2023.
Because some projections are outliers, we use a trimmed version of the weighted Harrell-Davis quantile estimator for greater robustness.

>>>>

The mode is the most common/frequent value.
The mode of the values of 0, 0, 10, 15, 20, 30, and 1000 is `{r} exampleValues_mode`.
The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `Mode()` function for computing the mode of a set of data.

If you want to give some values more weight to others, you can calculate a weighted mean and a weighted median (or other quantile), while assigning a weight to each value.
The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains various functions for computing the weighted median (i.e., a weighted quantile at the 0.5 quantile, which is equivalent to the 50th percentile) based on @Akinshin2023.
Because some projections are outliers, we use a trimmed version of the weighted Harrell-Davis quantile estimator for greater robustness.

@@

If you want to give some values more weight to others, you can calculate weighted quantiles, while assigning a weight to each value.
The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains various functions for computing weighted quantiles based on @Akinshin2023.
Because some projections are outliers, we use a trimmed version of the weighted Harrell-Davis quantile estimator for greater robustness.

### 2025-07-29 evaluating-prediction-accuracy.qmd
20250722 - link
20250722 - add URL
20250729 - update URLs

The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `accuracyAtCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables.

@@

The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `accuracyAtEachCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables at each possible cutoff.

@@

This section describes threshold-independent indexes of accuracy.
That is, each index of accuracy described in this section provides a single numerical index of accuracy that aggregates the accuracy across all possible cutoffs.
The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] contains the `accuracyOverall()` function that computes many threshold-independent accuracy indices.

@@

Note: MPE is undefined when one or more of the observed values equals zero, due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: MAPE is undefined when one or more of the observed values equals zero, due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: sMAPE is undefined when one or more of the individuals has a prediction–observed combination such that the sum of the absolute value of the predicted value and the absolute value of the observed value equals zero ($|\text{predicted}_i| + |\text{observed}_i|$), due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: Root mean squared log error is undefined when one or more predicted values or actual values equals −1.
When predicted or actual values are -1, this leads to $log(0)$, which is undefined.
The `accuracyOverall()` function of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.

>>>>

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `accuracyAtCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables.

@@

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `accuracyAtEachCutoff()` function that computes many accuracy indices for the prediction of categorical outcome variables at each possible cutoff.

@@

This section describes threshold-independent indexes of accuracy.
That is, each index of accuracy described in this section provides a single numerical index of accuracy that aggregates the accuracy across all possible cutoffs.
The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] contains the `accuracyOverall()` function that computes many threshold-independent accuracy indices.

@@

Note: MPE is undefined when one or more of the observed values equals zero, due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: MAPE is undefined when one or more of the observed values equals zero, due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: sMAPE is undefined when one or more of the individuals has a prediction–observed combination such that the sum of the absolute value of the predicted value and the absolute value of the observed value equals zero ($|\text{predicted}_i| + |\text{observed}_i|$), due to division by zero.
The `accuracyOverall()` function of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Note: Root mean squared log error is undefined when one or more predicted values or actual values equals −1.
When predicted or actual values are -1, this leads to $log(0)$, which is undefined.
The `accuracyOverall()` function of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] provides the option in the function to drop undefined values so you can still generate an estimate of accuracy despite undefined values.

@@

Below are estimates of projection accuracy and [calibration plots](#sec-calibrationPlot) for [seasonal](#sec-accuracyProjectionsSeasonal) and [weekly](#sec-accuracyProjectionsWeekly) projections.
FantasyFootballAnalytics.net also provides tools to evaluate the accuracy of historical projections [@FFA-accuracy]: <https://fantasyfootballanalytics.net/ffanalytics-web-app-accuracy-tab>.

### 2025-07-29 getting-started.qmd
20250729 - update URLs

The [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab] has a convenience function, `%ni%`, for the logical operator of determining whether an element is *not* in a value of another vector:

>>>>

The [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab] has a convenience function, `%ni%`, for the logical operator of determining whether an element is *not* in a value of another vector:

### 2025-07-29 machine-learning.qmd
20250729 - update URLs

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.
For each of the models, we fit and evaluate the models using the `tidymodels` ecosystem of packages [@R-tidymodels; @Kuhn2020_packages].
we specify our model formula using the `recipe()` function of the `recipes` package [@R-recipes].
We define the model using the `linear_reg()`, `set_engine()`, and `set_mode()` functions of the `parsnip` package [@R-parsnip].
We specify the workflow using the `workflow()`, `add_recipe()`, and `add_model()` functions of the `workflows` package [@R-workflows].
We fit the cross-validation model using the `fit_resamples()` function of the `tune` package [@R-tune].
We specify the accuracy metrics to evaluate using the `metric_set()` function of the `yardstick` package [@R-yardstick].
We fit the final model using the `fit()` function of the `workflows` package [@R-workflows].
We evaluate the accuracy of the model's predictions on the test data using the `accuracyOverall()` of the [`petersenlab`](https://github.com/DevPsyLab/petersenlab) package [@R-petersenlab].

>>>>

Below, we fit a linear regression model with one predictor and evaluate it with [cross-validation](#sec-crossValidation).
We also evaluate its accuracy on the hold-out (test) data.
For each of the models, we fit and evaluate the models using the `tidymodels` ecosystem of packages [@R-tidymodels; @Kuhn2020_packages].
we specify our model formula using the `recipe()` function of the `recipes` package [@R-recipes].
We define the model using the `linear_reg()`, `set_engine()`, and `set_mode()` functions of the `parsnip` package [@R-parsnip].
We specify the workflow using the `workflow()`, `add_recipe()`, and `add_model()` functions of the `workflows` package [@R-workflows].
We fit the cross-validation model using the `fit_resamples()` function of the `tune` package [@R-tune].
We specify the accuracy metrics to evaluate using the `metric_set()` function of the `yardstick` package [@R-yardstick].
We fit the final model using the `fit()` function of the `workflows` package [@R-workflows].
We evaluate the accuracy of the model's predictions on the test data using the `accuracyOverall()` of the [`petersenlab`](https://cran.r-project.org/web/packages/petersenlab/index.html) package [@R-petersenlab].
